Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-15 manuscript.tex
Update on Overleaf.

There are different solutions to provide with a distance between two given spike trains. A known measure is the Victor-Purpura distance, which  overcomes inconsistencies experienced with a simple firing rate (Poisson model) of spike trains~\citep{victor_nature_1996}. In a later study,~\citet{van_rossum_novel_2001} have defined a distance that uses a time constant as a parameter. Depending on this parameter, the distance interpolates between a coincidence detector and a rate difference counter. Such distances were extended to non-Euclidean metrics and use morphological manipulations to compute spike train dissimilarity~\citep{kreuz_measuring_2007}. Mathematically, the stability of distance measures induced by level-crossing sampling can be evaluated~\citep{moser_stability_2014}, notably in light of the so-called Weyl's discrepancy measure~\citep{weyl_ueber_1916}, which may lead to the definition of a cross-correlation measure which is adapted to the event-based nature of spiking signals. These observations lead to the intuition that each distance may be related as the optimal solution of a generative model for these measures, possibly through non-linear relations~\citep{aronov_non-euclidean_2004}. % ~\citep{}

>>>>

There are different solutions to provide with a distance between two given spike trains. A known measure is the Victor-Purpura distance, which  overcomes inconsistencies experienced with a simple firing rate (Poisson model) of spike trains~\citep{victor_nature_1996}. In a later study,~\citet{van_rossum_novel_2001} have defined a distance that uses a time constant as a parameter. Depending on this parameter, the distance interpolates between a coincidence detector and a rate difference counter. Such distances were extended to non-Euclidean metrics and use morphological manipulations to compute spike train dissimilarity~\citep{kreuz_measuring_2007}. Mathematically, the stability of distance measures induced by level-crossing sampling can be evaluated~\citep{moser_stability_2014}, notably in light of the so-called Weyl's discrepancy measure~\citep{weyl_ueber_1916}, which may lead to the definition of a cross-correlation measure which is adapted to the event-based nature of spiking signals. These observations lead to the intuition that each distance may be as well  as the optimal solution of a generative model for these measures, possibly through non-linear relations~\citep{aronov_non-euclidean_2004}. % ~\citep{}
